### 2021-02-24 evaluation.tex
Explain the importance of saturation loop iterations
Remove some useless content
Hide URLs into footnotes

The scripts that were used to generate the training data and to train and evaluate the recommender
are available at the following URL:
\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}
\todo{FB: Tag the version and link to the tag.}
\todo{FB: Add some wrapper scripts and readme for ease of use.}
\todo{MS: Obycejne schovavan URL do footnote, at tolik netrci!
Taky se da zkratit, napriklad pomoci \url{git.io}.}

@@

The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
\Vampire{} was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
The modified version of \Vampire{} is available at the following URL:
\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6} \todo{MS: nebo jeste lip. Slo by udelat repo, 
ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

@@

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).
\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}

@@

The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
\todo{FB: Consider joining with section Problem set below.}
\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
%New symbols may be introduced during preprocessing,
%namely due to the Tseitin transformation and Skolemization.
%We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
%where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
%and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.

>>>>

The scripts that were used to generate the training data and to train and evaluate the recommender
are available online.\footnote{\url{https://github.com/filipbartek/vampire-ml/tree/6907ee35}}
\todo{FB: Tag the version and link to the tag.}
\todo{FB: Add some wrapper scripts and readme for ease of use.}

@@

The empirical evaluation was performed using a modified version of the \gls{atp} \Vampire{} 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
\Vampire{} was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
\Vampire{} was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
The modified version of \Vampire{} is available online.\footnote{\url{https://github.com/filipbartek/vampire/tree/3bbfa9e6}} \todo{MS: nebo jeste lip. Slo by udelat repo, 
ve kterym bude textak, co vsechno vysvetli, vcetne linku na ty dve repa co zminujes tady a vyse.}

@@

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop (see \cref{sec:saturation}).

@@

The input problems are assumed to be specified in the \gls{cnf} or the \gls{fof} fragment
of the \acrshort{tptp} language \cite{Sutcliffe2017}.
% http://www.tptp.org/TPTP/SyntaxBNF.html
\Gls{fof} problems are first converted into equisatisfiable \gls{cnf} problems by \Vampire{}.
%New symbols may be introduced during preprocessing,
%namely due to the Tseitin transformation and Skolemization.
%We denote the preprocessed \gls{cnf} problem as $P = (\Sigma, \mathit{Cl})$,
%where $\Sigma$ denotes the list of all predicate and function symbols of the problem,
%and $\mathit{Cl}$ denotes a set of clauses over $\Sigma$ that constitute the problem.
